R Notebook

### 2022-04-29 Code/Simulation.Rmd
minor changes to figures

```{r}
# Load packages
library(tidyverse)
library(copula)
library(evd)
library(ismev)
source('tspb.R')
```

@@

```{r ARMA(1,1) D}
ptm <- proc.time()

@@

```{r hist_ma1_arma_ar2_D}
load('results_ma1_D.RData')
model <- rep("MA(1)", 2000)
ma1 <- data_frame(results, new_col)

load('results_arma_D.RData')
model <- rep("ARMA(1, 1)", 2000)
arma <- data_frame(results, new_col)

load('results_ar2_D.RData')
model <- rep("AR(2)", 2000)
ar2 <- data_frame(results, new_col)

>>>>

```{r packages}
# Load packages
library(tidyverse)
library(copula)
library(evd)
library(ismev)
source('tspb.R')
```

@@

```{r ARMA(1, 1) D}
ptm <- proc.time()

@@

```{r hist_ma1_arma_ar2_D}
load('results_ma1_D.RData')
model <- rep("MA(1)", 2000)
ma1 <- data_frame(results, model)

load('results_arma_D.RData')
model <- rep("ARMA(1, 1)", 2000)
arma <- data_frame(results, model)

load('results_ar2_D.RData')
model <- rep("AR(2)", 2000)
ar2 <- data_frame(results, model)
